Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-14 paper/paper.tex
Moved the figures to be in line with the text, gave them better captions.

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_1.png}
    \caption{Awesome Image}
    \label{fig:shadow_1}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_2.png}
    \caption{Awesome Image}
    \label{fig:shadow_2}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_1.png}
    \caption{Depicted is the light source, a sphere, and a ray of light tangent to the sphere (labeled as generatrix of cone).}
    \label{fig:shadow_1}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{sphere_shadow_figure_2.png}
    \caption{This figure includes in addition the perpendicular from the point of tangency to the axis of the cone. The distance $L''$ is from the light source to the intersection of this perpendicular with the axis.}
    \label{fig:shadow_2}
\end{figure}
